The COVID-19 Pandemic's Impact on Bullying Search Intensity with respect to Asian Population

### 2023-02-22 Outputs/Paper/paper.qmd
Added more discussion paragraphs

>>>>

## Bullying and Cyberbullying Searches Decreased During COVID-19

The COVID-19 pandemic saw a decrease in bullying and cyberbullying searches. Students were no longer learning in-person, so it is natural that bullying searches would decrease. However, cyberbullying searches also decreased despite students spending more time online with eachother. There are multiple factors attributing to the decrease of cyberbullying searches during COVID-19.

One factor is a steady increase of anti-bullying campaigns causing the gradual decrease in cyberbullying. Another factor is that outside of virtual classrooms, students are not spending time amongst their peers. Less exposure to one another leads to less confrontation and cyberbullying. One last factor is due to the digitization of student's lives during the pandemic, some students may have become desensitized to cyberbullying. What one student may perceive as cyberbullying, another would perceive as banter. The nuances of in-person communication is lost over digital communication, and these nuances lead to differences in perception.
